Guarded Recursion in Agda via Sized Types

### 2019-01-16 code-oneclock-paper/latex/paper.tex
Fixed affiliation

\author{Niels van der Weide}{Institute for Computation and Information Sciences, Radboud University, The Netherlands}{nweide@cs.ru.nl}{https://orcid.org/0000-0003-1146-4161}{}

>>>>

\author{Niels van der Weide}{Institute for Computation and Information Sciences, Radboud University, Nijmegen, The Netherlands}{nweide@cs.ru.nl}{https://orcid.org/0000-0003-1146-4161}{}
